Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.

### 2019-02-07 paper/snakemajoranas.tex
write about disorder vs geometry

>>>>

\comment{Disorder has a similar effect but one has no control over it.}
Recently, it has been shown~\cite{haim_double-edge_2018} that having a system with weak disorder can lead to a reduction in the Majorana decay length, similar to what happens with the introduction of a zigzag geometry.
However, in contrast to introducing weak disorder into a system, changing the geomerty is experimentally much easier to realize and therefore easier to control.
